
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{changepage}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeDescription}[1] {
  \vspace{0.25cm}
  \begin{adjustwidth}{0.5cm}{0.5cm}
    #1
  \end{adjustwidth}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newenvironment{header}{
  \setlength{\topsep}{0pt}\par\kern\topsep\centering\color{primaryColor}\linespread{1.5}
}{
  \par\kern\topsep
} % new environment for the header

% save the original href command in a new command:
\let\hrefWithoutArrow\href
% new command for external links:
\renewcommand{\href}[2]{\hrefWithoutArrow{#1}{\mbox{\ifthenelse{\equal{#2}{}}{ }{#2 }\raisebox{.15ex}{\footnotesize \faExternalLink*}}}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{header}
\fontsize{30 pt}{30 pt}
\textbf{Guilherme Steinert de Azevedo}

\vspace{0.3 cm}

\normalsize
\mbox{\hrefWithoutArrow{tel:+5548991894679}{{\footnotesize\faPhone*}\hspace*{0.13cm}+55 48 9189 4679}}
\hspace*{1.25cm}
\mbox{\hrefWithoutArrow{mailto:steinert999@outlook.com}{{\small\faEnvelope[regular]}\hspace*{0.13cm}steinert999@outlook.com}}
\hspace*{1.25cm}
\mbox{{\small\faMapMarker*}\hspace*{0.13cm}Santa Catarina, Brazil}
\hspace*{1.25 cm}
\mbox{\hrefWithoutArrow{https://linkedin.com/in/guilhermesteinert}{{\small\faLinkedinIn}\hspace*{0.13cm}guilhermesteinert}}
\hspace*{1.25 cm}
\mbox{\hrefWithoutArrow{https://github.com/Steinert999}{{\small\faGithub}\hspace*{0.13cm}Steinert999}}
\hspace*{1.25 cm}
\end{header}
%-----------ABOUT---------------------
\section{About}
\resumeDescription{
  With six years of experience in software development, I specialize in Java and Kotlin, currently focusing on microservices.\\
  I am completing my degree and seeking an environment that offers opportunities for continuous learning and growth.\\
  Determined to tackle new challenges, I am ready to contribute in an environment that values innovation and technical excellence.
}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Instituto de Ensino Superior da Grande Florianópolis}{Santa Catarina, Brazil}
      {Bachelor's Degree in Computer Science}{Jan. 2018 -- Dec. 2024}
    \resumeSubheading
      {Universidade do Vale do Itajaí}{Santa Catarina, Brazil}
      {Bachelor's Degree in Game Design and Digital Entertainment}{Apr. 2015 -- Jan. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Invillia}{(Remote) São Paulo, Brazil}
      {Middle Software Engineer}{Jan. 2022 - Present}
      \resumeItemListStart
        \resumeItem{Outsourcing for a financial company}
          {Working with microservices focused on authentication and clearing of financial transactions, requiring high availability and responsiveness.}
        \resumeItem{Used Technologies}
          {Java, Kotlin, Python, Spring, Kubernetes, RabbitMQ, Kafka, Splunk, Oracle, MySQL, MongoDB, New Relic, HashiCorp Vault, AWS S3, Scrum}
      \resumeItemListEnd

    \resumeSubheading
      {Capgemini}{(Remote) São Paulo, Brazil}
      {Middle Software Engineer}{Jun. 2021 - Jan. 2022}
      \resumeItemListStart
        \resumeItem{Outsourcing for government}
                   {Worked with systems focused on the DETRAN vehicle auction in Rio Grande do Sul.}
        \resumeItem{Used technologies}
          {Java, JPA, MySQL, Typescript, Angular, Spring, Node.js, CSS, HTML, GitLab, Scrum}
              \resumeItemListEnd

    \resumeSubheading
      {Zalf Sistemas}{(Remote) Santa Catarina, Brazil}
      {Middle Software Engineer}{Oct. 2020 -- Jun. 2021}
      \resumeItemListStart
        \resumeItem{Prolog App}
                   {Worked with Prolog; a system focused on fleet and tire management, acting in Brazil and Paraguay.}
        \vspace{-4mm}
        \resumeItem{Used technologies}
          {Java, Spring, JPA, PostgreSQL, PLSQL, Github, Docker, Scrum}
      \resumeItemListEnd

      \resumeSubheading
      {Brazil Direct Software}{Santa Catarina, Brazil}
      {Middle Software Engineer}{Aug. 2020 - Oct. 2020}
      \resumeItemListStart
      \resumeItem{Outsourcing for government}
                 {Worked with systems focused on State Department of Health of Santa Catarina.}
      \resumeItem{Used technologies}
                 {Java, Angular, Typescript, Spring, JSF, JSP, JPA, PostgreSQL, MySQL, GitLab, WildFly}
     \resumeItemListEnd
     \resumeSubheading
         {Brazil Direct Software}{Santa Catarina, Brazil}
         {Junior Software Engineer}{Oct. 2019 - Aug. 2020}
         \resumeItemListStart
         \resumeItem{Outsourcing for government}
                    {Worked with systems focused on State Department of Health of Santa Catarina.}
         \resumeItem{Used technologies}
                    {Java, Angular, Typescript, Spring, JSF, JSP, JPA, PostgreSQL, MySQL, GitLab, WildFly}
         \resumeItemListEnd
     \resumeSubheading
        {Nexxess Company}{Santa Catarina, Brazil}
        {Tech Support}{Dec. 2018 - Oct. 2019}
     \resumeItemListStart
     \resumeItem{Support with customer first contact}
                {Focused on a middleware between banks and companies financial transactions}
     \resumeItem{Used technologies}
                {Linux, Bash, Windows}
     \resumeItemListEnd
     \resumeSubheading
         {Nexxess Company}{Santa Catarina, Brazil}
         {Tech Support Trainee}{Oct. 2018 - Dec. 2018}
         \resumeItemListStart
         \resumeItem{Support with customer first contact}
                    {Focused on a middleware between banks and companies financial transactions}
                    \resumeItem{Used technologies}
                               {Linux, Bash, Windows}
                               \resumeItemListEnd

  \resumeSubHeadingListEnd
%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
     \item \textbf{Java}: aprox. 5 years
     \item \textbf{Kotlin}: aprox. 1 year
     \item \textbf{Typescript}: aprox. 2 years
     \item \textbf{SQL}: aprox. 5 years
     \item \textbf{PostgreSQL PLSQL}: aprox. 8 months
     \item \textbf{Python}: aprox. 1 year
     \item \textbf{Scrum}: aprox. 3 years
 \resumeSubHeadingListEnd

 %--------LANGUAGES------------
 \section{Languages}
 \resumeSubHeadingListStart
    \item{\textbf{Portuguese}{: Native}}
    \item{\textbf{English}{: Intermediate}}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
